---
title: "Yampa Valley 2022 CHNA Survey Analysis"
author: "Nicole Harty"
date: "4/11/2022"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    css: template.css

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lubridate)
library(likert)
library(kableExtra)
library(plotly)
library(janitor)
library(imager)
library(openxlsx)

source("SurveyDataCleanWrangle.R")


```


```{r label=logo}
htmltools::img(src = knitr::image_uri("RouttPHlogo.png"),
alt = 'logo',
style = 'position:absolute; top:105px; right:125px; padding:5px; width: 200px; height: 100px')
```

```{r label=NumbersToReference}
TotalRouttRespondents <- Demos %>% filter(County=="Routt") %>% summarise(n_distinct(ResponseID)) %>% pull()
```

A total of **`r Demos %>% summarise(n_distinct(ResponseID)) %>% pull()`** people responded to the Yampa Valley Community Health Needs Assessment Survey. Of these, **`r Demos %>% filter(County=="Routt") %>% summarise(n_distinct(ResponseID)) %>% pull()`** live in Routt County.  

# CHNA Survey Respondent Demographics  

```{r label=Demos, results='asis'}
DemosColumns <- ncol(Demos)
DemosColumnNames <- colnames(Demos)
for (i in 2:DemosColumns) {
  Demos %>%
    filter(County=="Routt") %>%
    group_by_at(i) %>%
    summarise(Count = n()) %>%
    mutate(Percentage = scales::percent(Count/sum(Count))) %>%
    arrange(Count) %>%
    kable(caption = paste0("Summary of Routt County CHNA Survey Respondents by ",DemosColumnNames[[i]])) %>%
    print()
}
```

# Response Summaries  

## Factors Important for Healthy Community
Includes data from the following survey questions:  

- Select the three most important factors for a Healthy Community.  
- Select the three most important factors for a Healthy Community. OPEN ENDED  
- Select the three factors which you feel you would like to see more of in Yampa Valley.  
- Select the three factors which you feel you would like to see more of in Yampa Valley. OPEN ENDED  
- Level of agreement with specific positive statements about the community.  

```{r label=Barriers}
HealthyCommunityFactors %>%
  pivot_longer(4:(ncol(HealthyCommunityFactors)), names_to = "IndivItems") %>%
  group_by(IndivItems) %>%
  summarise(Count = sum(value, na.rm = TRUE)) %>%
  mutate(Percentage = scales::percent(Count/TotalRouttRespondents)) %>%
  arrange(desc(Count)) %>%
  kable(caption = "Select the factors important to a healthy community (up to 3)")

```


## Health Problems  
Includes data from the following survey questions:  

- Select the three drugs misuse or abuse you are most concerned about.  
- Select the three drugs misuse or abuse you are most concerned about. OPEN ENDED  
- Select the three factors which you feel you would like to see more of in Yampa Valley.  
- Select the three factors which you feel you would like to see more of in Yampa Valley. OPEN ENDED  
- Level of agreement with specific positive statements about the community. 

## Access to Services  
Includes data from the following survey questions:  

Did you or your family need or use _____ in the past 12 months?   

- services for children/youth with emotional problems or delinquent behavior  
- treatment or counseling for alcohol or drug addiction   
- low- or no-cost dental/oral health services   
- mental health services   
- parenting information, training, or classes   
- child care/daycare financial assistance (including CCCAP)   
- physical or mental health care because of sexual assault or physical abuse   
- work-related/employment services (help finding work or job training)   
- financial assistance (unemployment, Colorado Works/TANF, Social Security)   
- housing services (rental/utility bill assistance, LEAP, or shelters)   
- transportation assistance services (vouchers, reimbursements)    


- Select all the reasons you did not receive the support or services you needed.  
- Select all the reasons you did not receive the support or services you needed. OPEN ENDED  
- On average, how much time does it take you to travel to see a doctor or other health care provider?  
- Select the challenges faced in getting the care you needed or wanted.  
- Select the challenges faced in getting the care you needed or wanted. OPEN ENDED  
- Have you avoided or delayed important health care services because of fear or discomfort?  
- Select all the reasons you were worried that your concerns would not be taken seriously or would not be treated fairly.  
- Select all the reasons you were worried that your concerns would not be taken seriously or would not be treated fairly. OPEN ENDED  
- Do you have a primary health care provider whom you see regularly?  
- What is your primary source of health care coverage?  
- What is your primary source of health care coverage? OPEN ENDED  
- About how long has it been since you last had health care coverage?           

```{r label=Barriers}
Barriers %>%
  pivot_longer(4:(ncol(Barriers)), names_to = "IndivItems") %>%
  group_by(IndivItems) %>%
  summarise(Count = sum(value, na.rm = TRUE)) %>%
  mutate(Percentage = scales::percent(Count/sum(Count))) %>%
  arrange(desc(Count)) %>%
  kable(caption = "Select the challenges faced in getting the care you needed or wanted (up to 3)")

```

## Community Resources  
Includes data from the following survey questions:  

- Select up to three places or people you turn to When you are sick or need health advice.  
- Select up to three places or people you turn to When you are sick or need health advice. OPEN ENDED  
- Select up to three places you go if you need help getting non-medical resources.  
- Select up to three places you go if you need help getting non-medical resources. OPEN ENDED  
- Which of the following best describes the services and resources you rely on in your community.  
- Which of the following best describes the services and resources you rely on in your community. OPEN ENDED"  
 
## Priority Areas  
Includes data from the following survey questions:  

- What are the top three areas of health and well-being would you want Yampa Valley to prioritize as it considers where to focus improvement efforts?  
- What are the top three areas of health and well-being would you want Yampa Valley to prioritize as it considers where to focus improvement efforts? OPEN ENDED  
- What does Yampa Valley need and/or need to do to ensure it is a place where all individuals can live up to their fullest potential?"    

## Satisfaction with Community  
Includes data from the following survey questions:  

- How satisfied are you with your own health?  
- How satisfied are you with your community's health?  
- How satisfied are you with the safety in your community?  
- How satisfied are you with getting the medical care you need?  
- How satisfied are you with getting the mental health or substance use care you need?  
- How satisfied are you with getting help during stressful times" 
 

## Sources of Worry and Stress  
Includes data from the following survey questions:  

- How often in the past 12 months were you worried or stressed about having enough money to buy nutritious meals?  
- How often in the past 12 months were you worried or stressed about paying your rent/mortgage?  
- How often in the past 12 months were you worried or stressed about paying for gas for a car or other transportation costs?  
- How often in the past 12 months were you worried or stressed about paying for utilities (electricity, water)?  
- How often in the past 12 months were you worried or stressed about having internet service?  
- How often in the past 12 months were you worried or stressed about having Phone/Cell phone service?  
- How often in the past 12 months were you worried or stressed about paying for clothing?  
- How often in the past 12 months were you worried or stressed about being able to afford the medical care you need?
 
## COVID Vaccine  
Includes data from the following survey questions:  

- Have you personally received at least one dose of the COVID-19 vaccine?  
- MAIN reason why you decided to get vaccinated for COVID-19.  
- MAIN reason why you decided to get vaccinated for COVID-19. OPEN ENDED  
- Main reason you have not gotten the COVID-19 vaccine.  
- Main reason you have not gotten the COVID-19 vaccine. OPEN ENDED"     
 


# Responses Stratified by Demographics  

## Factors Important for Healthy Community
Includes data from the following survey questions:  

- Select the three most important factors for a Healthy Community.  
- Select the three most important factors for a Healthy Community. OPEN ENDED  
- Select the three factors which you feel you would like to see more of in Yampa Valley.  
- Select the three factors which you feel you would like to see more of in Yampa Valley. OPEN ENDED  
- Level of agreement with specific positive statements about the community.  

## Health Problems  
Includes data from the following survey questions:  

- Select the three drugs misuse or abuse you are most concerned about.  
- Select the three drugs misuse or abuse you are most concerned about. OPEN ENDED  
- Select the three factors which you feel you would like to see more of in Yampa Valley.  
- Select the three factors which you feel you would like to see more of in Yampa Valley. OPEN ENDED  
- Level of agreement with specific positive statements about the community. 

## Access to Services  
Includes data from the following survey questions:  

Did you or your family need or use _____ in the past 12 months?    

- services for children/youth with emotional problems or delinquent behavior  
- treatment or counseling for alcohol or drug addiction   
- low- or no-cost dental/oral health services   
- mental health services   
- parenting information, training, or classes   
- child care/daycare financial assistance (including CCCAP)   
- physical or mental health care because of sexual assault or physical abuse   
- work-related/employment services (help finding work or job training)   
- financial assistance (unemployment, Colorado Works/TANF, Social Security)   
- housing services (rental/utility bill assistance, LEAP, or shelters)   
- transportation assistance services (vouchers, reimbursements)    

- Select all the reasons you did not receive the support or services you needed.  
- Select all the reasons you did not receive the support or services you needed. OPEN ENDED  
- On average, how much time does it take you to travel to see a doctor or other health care provider?  
- Select the challenges faced in getting the care you needed or wanted.  
- Select the challenges faced in getting the care you needed or wanted. OPEN ENDED  
- Have you avoided or delayed important health care services because of fear or discomfort?  
- Select all the reasons you were worried that your concerns would not be taken seriously or would not be treated fairly.  
- Select all the reasons you were worried that your concerns would not be taken seriously or would not be treated fairly. OPEN ENDED  
- Do you have a primary health care provider whom you see regularly?  
- What is your primary source of health care coverage?  
- What is your primary source of health care coverage? OPEN ENDED  
- About how long has it been since you last had health care coverage?           

## Community Resources  
Includes data from the following survey questions:  

- Select up to three places or people you turn to When you are sick or need health advice.  
- Select up to three places or people you turn to When you are sick or need health advice. OPEN ENDED  
- Select up to three places you go if you need help getting non-medical resources.  
- Select up to three places you go if you need help getting non-medical resources. OPEN ENDED  
- Which of the following best describes the services and resources you rely on in your community.  
- Which of the following best describes the services and resources you rely on in your community. OPEN ENDED"  
 
## Priority Areas  
Includes data from the following survey questions:  

- What are the top three areas of health and well-being would you want Yampa Valley to prioritize as it considers where to focus improvement efforts?  
- What are the top three areas of health and well-being would you want Yampa Valley to prioritize as it considers where to focus improvement efforts? OPEN ENDED  
- What does Yampa Valley need and/or need to do to ensure it is a place where all individuals can live up to their fullest potential?"    

## Satisfaction with Community  
Includes data from the following survey questions:  

- How satisfied are you with your own health?  
- How satisfied are you with your community's health?  
- How satisfied are you with the safety in your community?  
- How satisfied are you with getting the medical care you need?  
- How satisfied are you with getting the mental health or substance use care you need?  
- How satisfied are you with getting help during stressful times" 
 

## Sources of Worry and Stress  
Includes data from the following survey questions:  

- How often in the past 12 months were you worried or stressed about having enough money to buy nutritious meals?  
- How often in the past 12 months were you worried or stressed about paying your rent/mortgage?  
- How often in the past 12 months were you worried or stressed about paying for gas for a car or other transportation costs?  
- How often in the past 12 months were you worried or stressed about paying for utilities (electricity, water)?  
- How often in the past 12 months were you worried or stressed about having internet service?  
- How often in the past 12 months were you worried or stressed about having Phone/Cell phone service?  
- How often in the past 12 months were you worried or stressed about paying for clothing?  
- How often in the past 12 months were you worried or stressed about being able to afford the medical care you need?
 
## COVID Vaccine  
Includes data from the following survey questions:  

- Have you personally received at least one dose of the COVID-19 vaccine?  
- MAIN reason why you decided to get vaccinated for COVID-19.  
- MAIN reason why you decided to get vaccinated for COVID-19. OPEN ENDED  
- Main reason you have not gotten the COVID-19 vaccine.  
- Main reason you have not gotten the COVID-19 vaccine. OPEN ENDED"     
 
